Secure Composition of Robust and Optimising Compilers

### 2023-06-23 popl/main.tex
relwork

\section{Related Work}\label{sec:relwork}
\section{Conclusion}\label{sec:concl}

>>>>

\section{Related Work}\label{sec:relwork}

This section compares existing work with the one presented in this paper.
To this end, work on robust preservation criteria (\Cref{subsec:relw:seccomprtp}) and on other secure compiler criteria (\Cref{subsec:relw:seccompcrit}) is being looked at.
The case study of this paper (\Cref{sec:casestud:defs,sec:casestud:rtp}) implements measures for ensuring \gls{ms} as well as \gls{cct} and these are compared with previous work as well (\Cref{subsec:relw:msmechs,subsec:relw:cctmechs}).

\subsection{Secure Compilation as Robust Preservation}\label{subsec:relw:seccomprtp}

The robust preservation of properties as a compiler--level criterion has been analyzed extensively~\cite{abate2019jour,patrignani2021rsc,abate2021extacc,patrignani2022universal,patrignani2019survey,kruse2022csc}.
This work has made use of that previous work and formalized the compositionality aspect which has not been explored before.
While there exists a composition theorem~\cite{abate2019jour} already, that theorem is not concerned with composing robustly safe compilers, but rather program components and contexts.
The work relating robust preservation with universal composability~\cite{patrignani2022universal} is closest to what this paper presents.
The authors demonstrate a similar compositionality theorem to what is presented here (\Cref{sec:compcomp}).
However, they do not demonstrate the scalability of the approach in the context of a practical compilation chain.

\subsection{Other Secure Compilation Criteria}\label{subsec:relw:seccompcrit}

\MKin{category theory stuff}
\MKin{full abstraction -> not compositional}
\MKin{compositional compiler correctness?}

\subsection{Memory Safety Mechanisms}\label{subsec:relw:msmechs}

\cite{michael2023mswasm}

\subsection{Cryptographic Constant Time Mechanisms}\label{subsec:relw:cctmechs}

\section{Conclusion}\label{sec:concl}
